---
title: "Untitled"
author: "Fumin Li"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# load combined model results

# load delmonte test results

```{r}
for (i in 1:5) {
  file_path_pos <- paste0("/Users/fuminli/Desktop/HLA_TCR_clean/model/combined_model_I/split_", i, "/delmonte_test/test_pos_output/avg_predicted_scores.csv")
  
  file_path_neg <- paste0("/Users/fuminli/Desktop/HLA_TCR_clean/model/combined_model_I/split_", i, "/delmonte_test/test_neg_output/avg_predicted_scores.csv")

  assign(paste0("combined_model_delmonte_test_pos_", i), read.csv(file_path_pos))
  assign(paste0("combined_model_delmonte_test_neg_", i), read.csv(file_path_neg))
}
```

# cal delmonte auc

```{r}
combined_model_delmonte_auc_list <- list()
for (i in 1:5) {

  pos_scores <- get(paste0("combined_model_delmonte_test_pos_", i))$score 
  neg_scores <- get(paste0("combined_model_delmonte_test_neg_", i))$score  

  test_set <- data.frame(
    score = c(pos_scores, neg_scores),
    label = c(rep(1, length(pos_scores)), rep(0, length(neg_scores))) 
  )
  

  roc_obj <- roc(test_set$label, test_set$score)
  auc_value <- auc(roc_obj)

  combined_model_delmonte_auc_list[[i]] <- auc_value
}
```

# load emerson test results

```{r}
for (i in 1:5) {
  file_path_pos <- paste0("/Users/fuminli/Desktop/HLA_TCR_clean/model/combined_model_I/split_", i, "/emerson_test/test_pos_output/avg_predicted_scores.csv")
  
  file_path_neg <- paste0("/Users/fuminli/Desktop/HLA_TCR_clean/model/combined_model_I/split_", i, "/emerson_test/test_neg_output/avg_predicted_scores.csv")

  assign(paste0("combined_model_emerson_test_pos_", i), read.csv(file_path_pos))
  assign(paste0("combined_model_emerson_test_neg_", i), read.csv(file_path_neg))
}
```

# cal emerson auc

```{r}
combined_model_emerson_auc_list <- list()
for (i in 1:5) {

  pos_scores <- get(paste0("combined_model_emerson_test_pos_", i))$score 
  neg_scores <- get(paste0("combined_model_emerson_test_neg_", i))$score  

  test_set <- data.frame(
    score = c(pos_scores, neg_scores),
    label = c(rep(1, length(pos_scores)), rep(0, length(neg_scores))) 
  )
  

  roc_obj <- roc(test_set$label, test_set$score)
  auc_value <- auc(roc_obj)

  combined_model_emerson_auc_list[[i]] <- auc_value
}
```

# load tcga test results

```{r}
for (i in 1:5) {
  file_path_pos <- paste0("/Users/fuminli/Desktop/HLA_TCR_clean/model/combined_model_I/split_", i, "/tcga_test/test_pos_output/avg_predicted_scores.csv")
  
  file_path_neg <- paste0("/Users/fuminli/Desktop/HLA_TCR_clean/model/combined_model_I/split_", i, "/tcga_test/test_neg_output/avg_predicted_scores.csv")

  assign(paste0("combined_model_tcga_test_pos_", i), read.csv(file_path_pos))
  assign(paste0("combined_model_tcga_test_neg_", i), read.csv(file_path_neg))
}
```

# cal tcga auc

```{r}
combined_model_tcga_auc_list <- list()
for (i in 1:5) {

  pos_scores <- get(paste0("combined_model_tcga_test_pos_", i))$score 
  neg_scores <- get(paste0("combined_model_tcga_test_neg_", i))$score  

  test_set <- data.frame(
    score = c(pos_scores, neg_scores),
    label = c(rep(1, length(pos_scores)), rep(0, length(neg_scores))) 
  )
  

  roc_obj <- roc(test_set$label, test_set$score)
  auc_value <- auc(roc_obj)
  
  combined_model_tcga_auc_list[[i]] <- auc_value
}
```
# load delmonte model results

# load delmonte test results

```{r}
for (i in 1:5) {
  file_path_pos <- paste0("/Users/fuminli/Desktop/HLA_TCR_clean/model/delmonte_model_I/split_", i, "/delmonte_test/test_pos_output/avg_predicted_scores.csv")
  
  file_path_neg <- paste0("/Users/fuminli/Desktop/HLA_TCR_clean/model/delmonte_model_I/split_", i, "/delmonte_test/test_neg_output/avg_predicted_scores.csv")

  assign(paste0("delmonte_model_delmonte_test_pos_", i), read.csv(file_path_pos))
  assign(paste0("delmonte_model_delmonte_test_neg_", i), read.csv(file_path_neg))
}
```

# cal delmonte auc

```{r}
delmonte_model_delmonte_auc_list <- list()

for (i in 1:5) {

  pos_scores <- get(paste0("delmonte_model_delmonte_test_pos_", i))$score 
  neg_scores <- get(paste0("delmonte_model_delmonte_test_neg_", i))$score  

  test_set <- data.frame(
    score = c(pos_scores, neg_scores),
    label = c(rep(1, length(pos_scores)), rep(0, length(neg_scores))) 
  )
  

  roc_obj <- roc(test_set$label, test_set$score)
  auc_value <- auc(roc_obj)

  delmonte_model_delmonte_auc_list[[i]] <- auc_value
}
```

# load emerson test results

```{r}
for (i in 1:5) {
  file_path_pos <- paste0("/Users/fuminli/Desktop/HLA_TCR_clean/model/delmonte_model_I/split_", i, "/emerson_test/test_pos_output/avg_predicted_scores.csv")
  
  file_path_neg <- paste0("/Users/fuminli/Desktop/HLA_TCR_clean/model/delmonte_model_I/split_", i, "/emerson_test/test_neg_output/avg_predicted_scores.csv")

  assign(paste0("delmonte_model_emerson_test_pos_", i), read.csv(file_path_pos))
  assign(paste0("delmonte_model_emerson_test_neg_", i), read.csv(file_path_neg))
}
```

# cal emerson auc

```{r}
delmonte_model_emerson_auc_list <- list()
for (i in 1:5) {

  pos_scores <- get(paste0("delmonte_model_emerson_test_pos_", i))$score 
  neg_scores <- get(paste0("delmonte_model_emerson_test_neg_", i))$score  

  test_set <- data.frame(
    score = c(pos_scores, neg_scores),
    label = c(rep(1, length(pos_scores)), rep(0, length(neg_scores))) 
  )
  

  roc_obj <- roc(test_set$label, test_set$score)
  auc_value <- auc(roc_obj)
  
  delmonte_model_emerson_auc_list[[i]] <- auc_value
}
```

# load tcga test results

```{r}
for (i in 1:5) {
  file_path_pos <- paste0("/Users/fuminli/Desktop/HLA_TCR_clean/model/delmonte_model_I/split_", i, "/tcga_test/test_pos_output/avg_predicted_scores.csv")
  
  file_path_neg <- paste0("/Users/fuminli/Desktop/HLA_TCR_clean/model/delmonte_model_I/split_", i, "/tcga_test/test_neg_output/avg_predicted_scores.csv")

  assign(paste0("delmonte_model_tcga_test_pos_", i), read.csv(file_path_pos))
  assign(paste0("delmonte_model_tcga_test_neg_", i), read.csv(file_path_neg))
}
```

# cal tcga auc

```{r}
delmonte_model_tcga_auc_list <- list()
for (i in 1:5) {

  pos_scores <- get(paste0("delmonte_model_tcga_test_pos_", i))$score 
  neg_scores <- get(paste0("delmonte_model_tcga_test_neg_", i))$score  

  test_set <- data.frame(
    score = c(pos_scores, neg_scores),
    label = c(rep(1, length(pos_scores)), rep(0, length(neg_scores))) 
  )
  

  roc_obj <- roc(test_set$label, test_set$score)
  auc_value <- auc(roc_obj)
  

  delmonte_model_tcga_auc_list[[i]] <- auc_value
}
```

# load Original DePTH model's result on Emerson and Delmonte

# load delmonte test results

```{r}
for (i in 1:5) {
  file_path_pos <- paste0("/Users/fuminli/Desktop/HLA_TCR_clean/model/delmonte_model_I/split_", i, "/delmonte_test/ori_DePTH_pos_output/predicted_scores.csv")
  
  file_path_neg <- paste0("/Users/fuminli/Desktop/HLA_TCR_clean/model/delmonte_model_I/split_", i, "/delmonte_test/ori_DePTH_neg_output/predicted_scores.csv")

  assign(paste0("emerson_model_delmonte_test_pos_", i), read.csv(file_path_pos))
  assign(paste0("emerson_model_delmonte_test_neg_", i), read.csv(file_path_neg))
}
```

# cal delmonte auc

```{r}
emerson_model_delmonte_auc_list <- list()

for (i in 1:5) {

  pos_scores <- get(paste0("emerson_model_delmonte_test_pos_", i))$score 
  neg_scores <- get(paste0("emerson_model_delmonte_test_neg_", i))$score  

  test_set <- data.frame(
    score = c(pos_scores, neg_scores),
    label = c(rep(1, length(pos_scores)), rep(0, length(neg_scores))) 
  )
  

  roc_obj <- roc(test_set$label, test_set$score)
  auc_value <- auc(roc_obj)

  emerson_model_delmonte_auc_list[[i]] <- auc_value
}
```


# for emerson

```{r}
emerson_pairs_I <- read.csv("/Users/fuminli/Desktop/HLA_TCR_clean/data/emerson_pairs_I.csv")
roc_emerson_I <- roc(emerson_pairs_I$class, emerson_pairs_I$score)
```

# for tcga

```{r}
tcga_pairs_I <- read.csv("/Users/fuminli/Desktop/HLA_TCR_clean/data/tcga_pairs.csv")
roc_tcga_I <- roc(tcga_pairs_I$class, tcga_pairs_I$score)
```

```{r}
first_values <- c(combined_model_delmonte_auc_list[[3]], 
                  emerson_model_delmonte_auc_list[[3]],
                  delmonte_model_delmonte_auc_list[[3]],
                  combined_model_emerson_auc_list[[3]],
                  roc_emerson_I$auc,
                  delmonte_model_emerson_auc_list[[3]])

testing_data <- rep(c("Delmonte Test", "Emerson Test"), each = 3)
training_model <- rep(c("Combined Model", "Emerson Model", "Delmonte Model"), times = 2)
colors <- c("orange", "lightgreen", "lightblue")  # Combined Model和Delmonte Model的颜色
```

```{r}
adjusted_values = first_values - 0.5

par(font.main = 2,   
    font.lab = 2,   
    font.axis = 2,  
    font = 2)       

barplot(height = adjusted_values,
        beside = TRUE,           
        names.arg = testing_data,         
        col = colors[as.numeric(factor(training_model))], 
        main = "Emerson+Delmonte vs Emerson vs Delmonte",  
        xlab = "Testing Data",            
        ylab = "AUC",                 
        ylim = c(0, 0.5),                
        font.main = 2,               
        font.lab = 2,                 
        font.axis = 2,                 
        legend.text = unique(training_model),
        args.legend = list(x = "topright", inset = c(-0.05, -0.08)),
        space = c(0, 0, 0, 1),          
        xaxt = "n",                    
        yaxt = "n"                    
)

axis(2, at = seq(0, 0.5, by = 0.1), labels = seq(0.5, 1, by = 0.1))

axis(1, at = seq(1.5, 6, by = 3), labels = c("Delmonte Test", "                                  Emerson Test"), tick = FALSE)
```

```{r}
# 生成表格
# 生成排列组合
models <- c("Emerson", "Delmonte", "Emerson+Delmonte")
test_data <- c("Emerson", "Delmonte", "TCGA")

# 使用 expand.grid 生成组合
df <- expand.grid(Training = models, Testing = test_data)
```

```{r}
for (i in 1:5) {
  df[[paste0("Split", i)]] <- round(c(
    roc_emerson_I$auc,
    delmonte_model_emerson_auc_list[[i]],
    combined_model_emerson_auc_list[[i]],
    emerson_model_delmonte_auc_list[[i]],
    delmonte_model_delmonte_auc_list[[i]],
    combined_model_delmonte_auc_list[[i]],
    roc_tcga_I$auc,
    delmonte_model_tcga_auc_list[[i]],
    combined_model_tcga_auc_list[[i]]
  ), 2)
}

```

```{r}
# 使用 flextable 创建表格
flextable(df)
```

```{r}

```


